Title Goes Here

### 2024-05-13 analysis/paper/paper.qmd
investigating words of interest in the EEO

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)
```

>>>>

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability")

# prepare a dataframe to store the count of words of interest
df <- data.frame(matrix(ncol = length(community_word), 
                        nrow = 0))
colnames(df) <- community_word

for(i in 1: nrow(EEO_clean)){
  df[i, ] <- str_detect(EEO_clean[i, ], 
                   community_word)
}

# detect if the words of interest is present or not.
EEO_clean_community_word <- 
  bind_cols(EEO_clean, df) %>% 
  rowwise() %>% 
  mutate(community_word_tally = sum(c_across(all_of(community_word)), 
                                    na.rm = T))
